%==============================================================================
% Appendix B: Reproducibility and Verification
%==============================================================================
\section{Reproducibility and Verification}
\label{app:reproducibility}

This appendix documents the computational engine specifications and verification 
procedures to ensure reproducibility of the results presented in this paper.

%------------------------------------------------------------------------------
\subsection{Engine Specifications}
\label{app:engine_specs}

\subsubsection{DPPUv2 Engine Core v3}

The calculations in this paper are performed using DPPUv2 Engine Core v3, 
a symbolic computation engine implemented in Python with SymPy.

\begin{table}[H]
\centering
\caption{Engine specifications.}
\begin{tabular}{@{}ll@{}}
\toprule
Item & Specification \\
\midrule
Engine name & DPPUv2 Engine Core v3 \\
Language & Python 3.10+ \\
Symbolic library & SymPy 1.12+ \\
Numerical library & NumPy, SciPy \\
Parallelization & multiprocessing (for parameter scans) \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Modular architecture}

The engine consists of the following modules:

\begin{itemize}
  \item \texttt{DPPUv2\_engine\_core\_v3.py}: Core symbolic computation
  \item \texttt{DPPUv2\_parameter\_scan\_v3.py}: Parameter space scanning
  \item \texttt{DPPUv2\_runner\_*.py}: Topology-specific runners
  \item \texttt{DPPUv2\_visualize\_*.py}: Visualization tools
\end{itemize}

%------------------------------------------------------------------------------
\subsection{Sanity Checks}
\label{app:sanity_checks}

The engine performs automatic verification at each computational step. 
The following sanity checks are implemented:

\subsubsection{Metric compatibility}

After computing the Levi--Civita connection, the engine verifies:
\begin{equation}
  \nabla_c \eta_{ab} = \partial_c \eta_{ab} - \Gamma^d{}_{ca}\eta_{db} 
                      - \Gamma^d{}_{cb}\eta_{ad} = 0.
\end{equation}

For frame basis with constant $\eta_{ab} = \delta_{ab}$, this reduces to:
\begin{equation}
  \Gamma_{abc} + \Gamma_{bac} = 0.
\end{equation}

\subsubsection{Riemann tensor antisymmetry (three-stage verification)}

The Riemann tensor $R^a{}_{bcd}$ satisfies the following antisymmetry properties:

\paragraph{Stage 1: Antisymmetry in last two indices}
\begin{equation}
  R^a{}_{bcd} = -R^a{}_{bdc}.
\end{equation}

\paragraph{Stage 2: Antisymmetry in first two indices (after lowering)}
\begin{equation}
  R_{abcd} = -R_{bacd}.
\end{equation}

\paragraph{Stage 3: Pair exchange symmetry}
\begin{equation}
  R_{abcd} = R_{cdab}.
\end{equation}

The engine verifies all three properties and logs any violations.

\subsubsection{Torsion tensor verification}

For the torsion ansatz, the engine verifies:

\paragraph{T1 component:} Total antisymmetry
\begin{equation}
  T^{(1)}_{abc} = T^{(1)}_{[abc]}.
\end{equation}

\paragraph{T2 component:} Trace condition
\begin{equation}
  T^{(2)\lambda}{}_{\mu\lambda} = V_\mu.
\end{equation}

\subsubsection{NY density consistency}

The engine verifies the decomposition relation:
\begin{equation}
  N_{\FULL} = N_{\TT} - N_{\REE}.
\end{equation}

This is checked numerically at representative parameter points.

%------------------------------------------------------------------------------
\subsection{Verification Log Examples}
\label{app:verification_logs}

The following shows excerpts from verification logs generated during 
computation.

\subsubsection{$\Sthree \times \Sone$ verification}

\begin{lstlisting}[basicstyle=\ttfamily\footnotesize]
=== S3S1 MX Mode Verification ===
[PASS] Metric compatibility: max deviation = 0.0
[PASS] Riemann antisymmetry (stage 1): verified
[PASS] Riemann antisymmetry (stage 2): verified
[PASS] Riemann antisymmetry (stage 3): verified
[PASS] NY decomposition: N_FULL = N_TT - N_REE
[INFO] Ricci scalar: 2*(-V**2*r**2 - 9*eta**2 - 72*eta - 108)/(3*r**2)
[INFO] N_FULL: 2*V*(4 - eta)/r
\end{lstlisting}

\subsubsection{$\Tthree \times \Sone$ verification}

\begin{lstlisting}[basicstyle=\ttfamily\footnotesize]
=== T3S1 MX Mode Verification ===
[PASS] Metric compatibility: max deviation = 0.0
[PASS] Riemann antisymmetry (stage 1): verified
[PASS] Riemann antisymmetry (stage 2): verified
[PASS] Riemann antisymmetry (stage 3): verified
[PASS] NY decomposition: N_FULL = N_TT - N_REE
[INFO] Ricci scalar: -2*V**2/3 - 6*eta**2/R1**2
[INFO] N_FULL: -2*V*eta/R1
[NOTE] N_FULL = N_REE (degenerate case for flat background)
\end{lstlisting}

\subsubsection{$\Nilthree \times \Sone$ verification}

\begin{lstlisting}[basicstyle=\ttfamily\footnotesize]
=== Nil3S1 MX Mode Verification ===
[PASS] Metric compatibility: max deviation = 0.0
[PASS] Riemann antisymmetry (stage 1): verified
[PASS] Riemann antisymmetry (stage 2): verified
[PASS] Riemann antisymmetry (stage 3): verified
[PASS] NY decomposition: N_FULL = N_TT - N_REE
[INFO] Ricci scalar: (-4*R**2*V**2 - 36*eta**2 + 24*eta + 9)/(6*R**2)
[INFO] N_FULL: -2*V*(3*eta + 1)/(3*R)
\end{lstlisting}

%------------------------------------------------------------------------------
\subsection{Cross-Validation}
\label{app:cross_validation}

\subsubsection{Analytical vs.\ numerical comparison}

For selected parameter points, we compare analytically derived $\Veff(r)$ 
expressions with direct numerical evaluation:

\begin{table}[H]
\centering
\caption{Analytical vs.\ numerical comparison at test points.}
\begin{tabular}{@{}lcccc@{}}
\toprule
Topology & $(V, \eta, \theta_{\NY})$ & $r$ & $\Veff^{\text{(anal)}}$ & 
$\Veff^{\text{(num)}}$ \\
\midrule
$\Sthree$ & $(2, -4, 1)$ & 1.0 & $-473.74$ & $-473.74$ \\
$\Sthree$ & $(2, -4, 1)$ & 2.0 & $-631.65$ & $-631.65$ \\
$\Tthree$ & $(2, -3, 1)$ & 1.0 & $1263.31$ & $1263.31$ \\
$\Nilthree$ & $(2, 0.5, 1)$ & 0.5 & $-128.30$ & $-128.30$ \\
\bottomrule
\end{tabular}
\end{table}

Agreement to machine precision confirms consistency between symbolic 
derivation and numerical evaluation.

\subsubsection{Limiting case verification}

The engine verifies correct behavior in limiting cases:

\paragraph{$\theta_{\NY} \to 0$ limit:}
NY contribution vanishes, recovering pure EC theory results.

\paragraph{$\eta \to 0$, $V \to 0$ limit:}
Torsion vanishes, recovering Levi--Civita (GR) results.

\paragraph{$\Tthree$ with $C^i{}_{jk} = 0$:}
Recovers flat space results with $R_{\LC} = 0$.

For details on the computational environment and software dependencies, 
see Appendix~\ref{app:access}.

