%==============================================================================
% Topology-Dependent Phase Classification of Effective Potentials
% in Einstein--Cartan + Nieh--Yan Minisuperspace
%==============================================================================
\documentclass[12pt,a4paper]{article}

%------------------------------------------------------------------------------
% Packages
%------------------------------------------------------------------------------
% Math
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{mathtools}
\usepackage{bm}

% Graphics and figures
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}

% Tables
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{multirow}

% TikZ for diagrams
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, calc, fit, backgrounds}

% Layout and formatting
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\onehalfspacing

% References and links
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{cleveref}

% Code listings (for appendices)
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  language=Python
}

% section break
\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}

% Misc
\usepackage{enumitem}
\usepackage{xcolor}

%------------------------------------------------------------------------------
% Custom commands
%------------------------------------------------------------------------------
% Math shortcuts
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Veff}{V_{\mathrm{eff}}}
\newcommand{\Ric}{R}
\newcommand{\LC}{\mathrm{LC}}
\newcommand{\EC}{\mathrm{EC}}
\newcommand{\NY}{\mathrm{NY}}
\newcommand{\TT}{\mathrm{TT}}
\newcommand{\REE}{\mathrm{REE}}
\newcommand{\FULL}{\mathrm{FULL}}

% Topology notation
\newcommand{\Sthree}{S^3}
\newcommand{\Tthree}{T^3}
\newcommand{\Nilthree}{\mathrm{Nil}^3}
\newcommand{\Sone}{S^1}

% Differential forms
\newcommand{\wedgep}{\wedge}

%------------------------------------------------------------------------------
% Title and authors
%------------------------------------------------------------------------------
\title{Topology-Dependent Phase Classification of Effective Potentials\\
in Einstein--Cartan + Nieh--Yan Minisuperspace}

\author{Muacca}

\date{\today}

%==============================================================================
\begin{document}
%==============================================================================

\maketitle

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
\begin{abstract}
We study Einstein--Cartan (EC) gravity supplemented with the Nieh--Yan (NY) term 
in a Euclidean--signature minisuperspace framework, and classify the resulting 
effective potential into distinct ``phases.'' Based on the presence or absence 
of local minima and barriers in the effective potential, we define three types: 
(I) metastable well with barrier, (II) barrier-free rolling, and 
(III) unstable/boundary-attached configurations.

While the Nieh--Yan density (a 4-form) can be written as an exact derivative, 
it is geometrically defined through the coframe and torsion. To facilitate 
meaningful comparison, we evaluate topology dependence under a unified ansatz. 
We adopt spatial sections that admit left-invariant coframes, enabling 
systematic description within a common minisuperspace framework.

As concrete test beds, we consider: (i) $\Sthree$, (ii) $\Tthree$, and 
(iii) $\Nilthree$. For the NY term, we focus on the complete form (FULL) 
as the primary object, while also examining TT (torsion-torsion component only) 
and REE (the remaining component) as diagnostic comparisons to disentangle 
the contributions within FULL.

Our investigation addresses two main questions: (1) How does the phase 
(Type I/II/III) of the effective potential depend on topology? 
(2) Can we identify, through numerical scanning, critical conditions 
corresponding to well formation/disappearance and barrier collapse, 
and organize their geometric dependence?

Our scanning results suggest the following:
\begin{itemize}
  \item The phase structure of the effective potential varies systematically 
        with topology.
  \item Within the NY term, some contributions exhibit relative insensitivity 
        to topology, while others appear selectively depending on geometric conditions.
\end{itemize}
\end{abstract}

%------------------------------------------------------------------------------
% Main text
%------------------------------------------------------------------------------
\input{sections/sec1}  % Introduction
\input{sections/sec2}  % Setup and conventions
\input{sections/sec3}  % Topology-specific reductions
\input{sections/sec4}  % Numerical results
\input{sections/sec5}  % Mechanisms and interpretation
\input{sections/sec6}  % Representative points and stability quality
\input{sections/sec7}  % Interpretation and utility
\input{sections/sec8}  % Conclusions and outlook

%------------------------------------------------------------------------------
% Acknowledgments
%------------------------------------------------------------------------------
\section*{Acknowledgments}

The author acknowledges the use of the following AI tools during manuscript preparation: 
Claude Opus 4.5 (Anthropic; accessed 2025-12), Gemini 3 Pro (Google; accessed 2025-12), 
Grok 4.1 Thinking (xAI; accessed 2025-12), and GPT-5.2 Thinking via ChatGPT (OpenAI; accessed 2025-12). 
These tools were used for language editing (including Japanese-English translation), outlining and 
improving exposition, drafting and reviewing auxiliary code (scripts and pseudocode) that was 
subsequently tested and validated by the author, and proposing candidate consistency checks and 
alternative derivations to be independently verified by the author. 
They were additionally used for literature discovery support (keyword generation and 
preliminary summaries of candidate papers); 
all references and factual claims were verified by the author using primary sources.

The AI tools did not determine the scientific claims of this work and were not used to generate or 
modify research data or evidentiary figures. 
The author takes full responsibility for the content and for any remaining errors.

This work was developed within the informal collaborative project \textbf{DPPU}
(\textbf{D}onut-like topology, \textbf{P}lanck-scale compactness,
\textbf{P}recession dynamics, \textbf{U}niverse).

%------------------------------------------------------------------------------
% Appendices
%------------------------------------------------------------------------------
\appendix
\input{appendices/appA}  % Theoretical details
\input{appendices/appB}  % Reproducibility and verification
\input{appendices/appC}  % Numerical computation details
\input{appendices/appD}  % Visualization tools
\input{appendices/appE}  % Volume rescaling invariance in T3×S1
\input{appendices/appF}  % Code and data access

%------------------------------------------------------------------------------
% References
%------------------------------------------------------------------------------
\bibliographystyle{unsrt}
% \bibliography{references}  % Uncomment when bibliography file is available

% Placeholder references
\begin{thebibliography}{99}
\bibitem{Hehl1976}
F.~W.~Hehl, P.~von der Heyde, G.~D.~Kerlick, and J.~M.~Nester,
``General relativity with spin and torsion: Foundations and prospects,''
Rev.\ Mod.\ Phys.\ \textbf{48}, 393 (1976).

\bibitem{Chandia1997}
O.~Chandia and J.~Zanelli,
``Topological invariants, instantons, and the chiral anomaly on spaces with torsion,''
Phys.\ Rev.\ D \textbf{55}, 7580 (1997).

\bibitem{NiehYan1982}
H.~T.~Nieh and M.~L.~Yan,
``An identity in Riemann-Cartan geometry,''
J.\ Math.\ Phys.\ \textbf{23}, 373 (1982).
\end{thebibliography}

%==============================================================================
\end{document}
%==============================================================================
